---
title: "Imputation - Imani"
author: "Imani C."
date: "July 1, 2018"
output: html_document
---
View(country)
```{r}
library(mice)
#seperates indv from other data
merge_imp <-big_merge[c(2,13,27:80)]
#turns everything to a factor
merge_imp<-as.data.frame(lapply(merge_imp,factor))

#merge_imp2 <- merge_imp %>% select((`meansOfControlDebtBondage`:`recruiterRelationUnknown`))

#merge_imp <- subset(merge_imp, factor < 2)

#merge_imp2 <- merge_imp[, sapply(merge_imp, function(col)  length(levels(col))) < 2]

#merge_imp2 <- merge_imp[, is.na(merge_imp2)]


#groups variables together
controlgroup <-names(merge_imp)[8:24]

labourgroup<-names(merge_imp)[c(26,27,33:44)] #includes issexexploit and #is forces labor, and is sex and labour 

issexgroup <- names(merge_imp)[46:49] #different sexual exploitation 

relationgroup <- names(merge_imp)[52:55] # recruiter relations columns

isgroup <- names (merge_imp)[c(30:33,50)] #Other types of imputatin that for some reaso have a high correlation

block_list <- list(c(controlgroup),c(labourgroup),c(issexgroup),c(relationgroup),c(isgroup)) 


ind_imp<- mice(merge_imp, maxit=0, blocks=list(c(controlgroup),c(labourgroup),c(relationgroup), c(issexgroup),c(isgroup),"meansOfControlNotSpecified","typeOfLabourNotSpecified", "recruiterRelationUnknown", "isOtherExploit","isSexAndLabour","majorityStatus","ageBroad", "gender", "majorityStatusAtExploit","majorityEntry","Country.of.Citizenship.y","Country.of.Exploitation.y"))

mat1<- ind_imp$predictorMatrix

#takesout Sex/Labor varaible
mat1[,27]<-0



method <- ind_imp$method
method[1:5] <- "logreg"


ind_imp2 <-mice(merge_imp, predictorMatrix = mat1, method=method, blocks = list(c(controlgroup),c(labourgroup),c(relationgroup), c(issexgroup),c(isgroup),"meansOfControlNotSpecified","typeOfLabourNotSpecified", "recruiterRelationUnknown", "isOtherExploit","isSexAndLabour","majorityStatus","ageBroad", "gender", "majorityStatusAtExploit","majorityEntry","Country.of.Citizenship.y","Country.of.Exploitation.y"))

ind_imp2
```



#work based on the email


2, Isolating columsn wtih only 1 factor levels
```{r}
merge_imp <-big_merge[c(2,13,27:80)]
#turns everything to a factor
merge_imp<-as.data.frame(lapply(merge_imp,factor))



merge_imp2 <- merge_imp[, sapply(merge_imp, function(col)  length(levels(col))) < 2] #meansOfControlFalsePRomises is the onyl column with NA'a and 1



```


3. Labor, Recruiter, and means of control (I do not think that the other categories can use this type of logic in terms of filling in NA's)

MAke sepearte vectors of each of the columns of these groups. USE grep to see repititions 


4.What are the two options?????? 

5. 
General blocks should be the same as seen above in my mice blockss



