---
title: "Regression Implementation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Some Preliminaries 

Loading the require libraries, functions and data:
```{r}
sure_path <- "/Users/shiva/code/CMU/sure2018"
load(paste(sure_path, "/data/mice_new_obj_marginal.Rdata", sep = ""))
library(tidyverse)
library(rpart)
library(caret)
library(ResourceSelection)
library(randomForest)
source(paste(sure_path, "/functions/mice_glm_function.R", sep = ""))
source(paste(sure_path, "/functions/beta_functions.R", sep = ""))
source('~/code/CMU/sure2018/functions/roc_functions.R')
```

Grabbing the imputed datasets from the mice new object:
We also create a new response variable from isForcedLabour and isSexualExploit
```{r}
#Here we loaded mice_new_obj_marginal but the code should work for any of the mice
#new objects this block lets the rest of the code remain general
working_mno <- mice_new_obj_marginal

working_mno <- bind_country_cols(working_mno, 10, 5, sure_path = sure_path)

for(i in 1:5){
  working_mno[["data_list"]][[10]][[i]][["data_corrected"]][["isForcedLabour"]] <-
    working_mno[["data_list"]][[10]][[i]][["data"]][["isForcedLabour"]]
  working_mno[["data_list"]][[10]][[i]][["data_corrected"]][["isSexualExploit"]] <-
    working_mno[["data_list"]][[10]][[i]][["data"]][["isSexualExploit"]]
}

data_list <- mice_sep(working_mno, 10, 5, stratify = TRUE, 
                      strat_vars = c("gender", "ageBroad", "Country_of_Exploit_2L",
                                     "Country_of_Citizenship_2L"))

#Building a composite variable LabourOrSex from isForcedLabour and isSexualExploit
#A 1 corresponds to Forced Labour and 0 to Sexual Exploitation
# for(set in c("training", "test")){
#   for(i in 1:5){
#     holder_df <- data_list[["data"]][[set]][[i]]
#     
#     holder_df$LabourOrSex <- holder_df$isForcedLabour 
#     
#     
#     holder_df[holder_df$isForcedLabour == 1 ,"LabourOrSex"] <- 2L
#     holder_df[holder_df$isSexualExploit == 1,"LabourOrSex"] <- 1L
#     holder_df[,"LabourOrSex"] <- as.factor(unlist(holder_df[,"LabourOrSex"])*1)
#     data_list[["data_corrected"]][[set]][[i]] <- holder_df
#   }
# }
```

## Creating the regression formulas

Here we construct formula objects to be passed into our regression function.
We want try to model the 
$$LabourOrSex \sim Age*Gender \: + \: CitzFeatures\: + \: ExpFeatures \: + \: MeansOfControl \: + \: RecruiterRelationship$$

```{r}
load(paste(sure_path, "/data/mice_new_obj.Rdata", sep = ""))
column_names <- colnames(mice_new_obj[['data_list']][[10]][[1]][['data']])
rm("mice_new_obj")
citz_features <- grep("Citz_+", column_names, value = TRUE) %>% paste(collapse = " + ")
exp_features <- grep("Exp_+", column_names, value = TRUE) %>% paste(collapse = " + ")
meansOfControl <- grep("meansOfControl+", column_names, value = TRUE)[-18] %>% paste(collapse = " + ")
migration <- grep("Migration_+", column_names, value = TRUE) %>% paste(collapse = " + ")
populationgroup <- grep("Population_+", column_names, value = TRUE) %>% paste(collapse = " + ")
RecruiterRelationship <- c(grep("recruiterRelation+", column_names, value = TRUE)[-5], 
                           "isAbduction") %>% paste(collapse = " + ")

imp_formula_labour <- paste("isForcedLabour ~ gender + ageBroad", citz_features, exp_features,
                     meansOfControl, migration, populationgroup, RecruiterRelationship,
                    sep = " + ") %>% as.formula()

imp_formula_labour_interaction <- paste("isForcedLabour ~ gender*ageBroad", citz_features, 
                                        exp_features, meansOfControl, migration, populationgroup,
                                        RecruiterRelationship,sep = " + ") %>% as.formula()

imp_formula_sex <- paste("isSexualExploit ~ gender + ageBroad", citz_features, exp_features,
                     meansOfControl, migration, populationgroup, RecruiterRelationship,
                    sep = " + ") %>% as.formula()

imp_formula_sex_interaction <- paste("isSexualExploit ~ gender*ageBroad", citz_features, 
                                        exp_features, meansOfControl, migration, populationgroup,
                                        RecruiterRelationship,sep = " + ") %>% as.formula()

imp_formula_comp <- paste("LabourOrSex ~ gender + ageBroad", citz_features, exp_features,
                     meansOfControl, migration, populationgroup, RecruiterRelationship,
                    sep = " + ") %>% as.formula()

imp_formula_comp_interaction <- paste("LabourOrSex ~ gender*ageBroad", citz_features, 
                                        exp_features, meansOfControl, migration, populationgroup,
                                        RecruiterRelationship,sep = " + ") %>% as.formula()

```


#Logistic Regression Model
###Running six sets of logistic regression models
```{r}
#Forced Labour
glm_labour_list <- mno_regression(data_list[["data_corrected"]][["training"]], 
                           imp_formula_labour, glm, family = "binomial")

glm_labour_interaction_list <- mno_regression(data_list[["data_corrected"]][["training"]], 
                           imp_formula_labour_interaction, glm, family = "binomial")

#Sexual Exploitation
glm_sex_list <- mno_regression(data_list[["data_corrected"]][["training"]], 
                           imp_formula_sex, glm, family = "binomial")

glm_sex_interaction_list <- mno_regression(data_list[["data_corrected"]][["training"]], 
                           imp_formula_sex_interaction, glm, family = "binomial")

```

### Evaluating the models
Looking at the Forced Labour model
```{r}
##The model without interactions
labour_betas <- beta_matrix(glm_labour_list)

#Visualizing the beta matrix
vis_beta_mat(labour_betas[,1:5])
#and getting approximating the variance in the parameters due to imputation
labour_betas_variance <- apply(labour_betas, MARGIN = 2, var)

#build ROC Curves for each labour model
labour_roc_df_list <- list()
for(i in 1:length(glm_labour_list)){
  labour_roc_df_list[[as.character(i)]][["prob"]] <- predict(glm_labour_list[[1]], 
                                                    type = "response",
                                                    newdata = data_list[["data_corrected"]][["test"]][[i]])
  
labour_roc_df_list[[as.character(i)]][["labels"]] <- data_list[["data_corrected"]][["test"]][[i]][["isForcedLabour"]]
  
  labour_roc_df_list[[as.character(i)]][["prob"]] <-
    labour_roc_df_list[[as.character(i)]][["prob"]][!is.na(labour_roc_df_list[[as.character(i)]][["labels"]])]
  
  labour_roc_df_list[[as.character(i)]][["labels"]] <-
    labour_roc_df_list[[as.character(i)]][["labels"]][!is.na(labour_roc_df_list[[as.character(i)]][["labels"]])]
}
labour_roc_df <- create_roc_df(labour_roc_df_list)

vis_roc_df(labour_roc_df)


#build ROC Curve for labour interaction model
labour_interaction_roc_df_list <- list()
for(i in 1:length(glm_labour_interaction_list)){
  labour_interaction_roc_df_list[[as.character(i)]][["prob"]] <- predict(glm_labour_interaction_list[[1]], 
                                                    type = "response",
                                                    newdata = data_list[["data_corrected"]][["test"]][[i]])
  
labour_interaction_roc_df_list[[as.character(i)]][["labels"]] <- data_list[["data_corrected"]][["test"]][[i]][["isForcedLabour"]]
  
  labour_interaction_roc_df_list[[as.character(i)]][["prob"]] <-
    labour_interaction_roc_df_list[[as.character(i)]][["prob"]][!is.na(labour_interaction_roc_df_list[[as.character(i)]][["labels"]])]
  
  labour_interaction_roc_df_list[[as.character(i)]][["labels"]] <-
    labour_interaction_roc_df_list[[as.character(i)]][["labels"]][!is.na(labour_interaction_roc_df_list[[as.character(i)]][["labels"]])]
}
labour_interaction_roc_df <- create_roc_df(labour_interaction_roc_df_list)

vis_roc_df(labour_roc_df)
vis_roc_df(labour_interaction_roc_df)

hoslem.test(data_list[["data_corrected"]][["test"]][[i]][["isForcedLabour"]],
              predict(glm_labour__list[[1]], type = "response", 
                      newdata = data_list[["data_corrected"]][["test"]][[1]])) %>%
    print

for(i in 1:length(glm_labour_list)){
  cat("Holsem GOF test for the", i, "th imputation")
  hoslem.test(data_list[["data_corrected"]][["test"]][[i]][["isForcedLabour"]],
              predict(glm_labour_list[[i]], type = "response", 
                      newdata = data_list[["data_corrected"]][["test"]][[i]])) %>%
    print
}

##The model with interaction 
labour_interaction_betas <- beta_matrix(glm_labour_interaction_list)

#Visualizing the beta matrix
vis_beta_mat(labour_interaction_betas)

#and getting approximating the variance in the parameters due to imputation
labour_interaction_betas_variance <- apply(labour_interaction_betas, MARGIN = 2, var)

#build ROC Curves for each model
roc_labour_interaction_list <- list()
for(i in 1:length(glm_labour_interaction_list)){
  roc_labour_interaction_list[[i]] <-
    pROC::roc(data_list[["data_corrected"]][["test"]][[i]][["isForcedLabour"]],
                        predict(glm_labour_interaction_list[[i]], type = "response", 
                                newdata = data_list[["data_corrected"]][["test"]][[i]]))
}
for(i in 1:length(glm_labour_interaction_list)){
  pROC::auc(roc_labour_interaction_list[[i]]) %>% print
}
for(i in 1:length(glm_labour_interaction_list)){
  cat("Holsem GOF test for the", i, "th imputation")
  hoslem.test(data_list[["data_corrected"]][["training"]][[i]][["isForcedLabour"]],
              predict(glm_labour_interaction_list[[i]], type = "response", 
                      newdata = data_list[["data_corrected"]][["training"]][[i]])) %>%
    print
}
```

Looking at the Sexual Exploitation model
```{r}
##The model without interactions
sex_betas <- beta_matrix(glm_sex_list)

#Visualizing the beta matrix
vis_beta_mat(sex_betas)

#and getting approximating the variance in the parameters due to imputation
sex_betas_variance <- apply(sex_betas, MARGIN = 2, var)

#build ROC Curves for each model
roc_sex_list <- list()
for(i in 1:length(glm_sex_list)){
  roc_sex_list[[i]] <-
    pROC::roc(data_list[["data_corrected"]][["test"]][[i]][["isSexualExploit"]],
                        predict(glm_sex_list[[i]], type = "response", 
                                newdata = data_list[["data_corrected"]][["test"]][[i]]))
}

for(i in 1:length(glm_sex_list)){
  cat("Hosmer-Lemeshow GOF test for the", i, "th imputation")
  hoslem.test(data_list[["data_corrected"]][["test"]][[i]][["isSexualExploit"]],
              predict(glm_sex_list[[i]], type = "response", 
                      newdata = data_list[["data_corrected"]][["test"]][[i]])) %>%
    print
}

##The model with interaction 
sex_interaction_betas <- beta_matrix(glm_sex_interaction_list)

#Visualizing the beta matrix
vis_beta_mat(sex_interaction_betas)

#and getting approximating the variance in the parameters due to imputation
sex_interaction_betas_variance <- apply(sex_interaction_betas, MARGIN = 2, var)

#build ROC Curves for each model
roc_sex_interaction_list <- list()
for(i in 1:length(glm_sex_interaction_list)){
  roc_sex_interaction_list[[i]] <-
    pROC::roc(data_list[["data_corrected"]][["test"]][[i]][["isSexualExploit"]],
                        predict(glm_sex_interaction_list[[i]], type = "response", 
                                newdata = data_list[["data_corrected"]][["test"]][[i]]))
}

for(i in 1:length(glm_sex_interaction_list)){
  cat("Holsem GOF test for the", i, "th imputation")
  hoslem.test(data_list[["data_corrected"]][["test"]][[i]][["isSexualExploit"]],
              predict(glm_sex_interaction_list[[i]], type = "response", 
                      newdata = data_list[["data_corrected"]][["test"]][[i]])) %>%
    print
}
```

##Hypothesis Testing
```{r}
slim_formula_exp <- paste("isForcedLabour ~ gender*ageBroad", citz_features, exp_features,
                       meansOfControl, migration, populationgroup, RecruiterRelationship,
                      sep = " + ") %>% gsub(pattern = "(\\ \\+\\ Exp_Tier)", replacement = "") %>%
      as.formula()

slim_formula_citz <- paste("isForcedLabour ~ gender*ageBroad", citz_features, exp_features,
                       meansOfControl, migration, populationgroup, RecruiterRelationship,
                      sep = " + ") %>% gsub(pattern = "(\\ \\+\\ Citz_Tier)", replacement = "") %>%
      as.formula()

slim_glm_exp <- glm(slim_formula_exp, family = "binomial", 
                    data = data_list[["data_corrected"]][["training"]][[1]])
anova(slim_glm_exp, glm_labour_interaction_list[[1]], test = "LRT")


slim_glm_citz <- glm(slim_formula_citz, family = "binomial", 
                    data = data_list[["data_corrected"]][["training"]][[1]])

anova(slim_glm_citz, glm_labour_interaction_list[[i]], test = "LRT")

#Sequential Hypothesis testing for each model:
for(i in 1:5){
  slim_glm_exp <- glm(slim_formula_exp, family = "binomial", 
                    data = data_list[["data_corrected"]][["training"]][[i]])
  anova(slim_glm_exp, glm_labour_interaction_list[[i]], test = "LRT") %>% print()
  
  slim_glm_citz <- glm(slim_formula_citz, family = "binomial", 
                    data = data_list[["data_corrected"]][["training"]][[i]])
  anova(slim_glm_citz, glm_labour_interaction_list[[i]], test = "LRT") %>% print()
  
  coef(summary(glm_labour_interaction_list[[i]]))[c(15:16, 24:25, 47:49),] %>% print()
}
```

##Stepwise regression
Warning this chunk takes a while. Each loop took about an hour and a half running from 
R Console on my computer
```{r}
# step_labour_interaction <- list()
# i <- 0
# for(imp_df in data_list[["data_corrected"]][["training"]]){
#   i <- i + 1
#   full_glm <- glm(formula = imp_formula_labour_interaction, data = imp_df, family = binomial)
#   step_labour_interaction[[i]] <- step(full_glm, direction = "both")
# }
# save(step_labour_interaction, file = paste(sure_path,
#                                            "/data/step_labour_interaction.Rdata", sep = ""))
# 
# step_comp_interaction <- list()
# i <- 0
# for(imp_df in data_list[["data_corrected"]][["training"]]){
#   i <- i + 1
#   full_glm <- glm(formula = imp_formula_comp_interaction, data = imp_df, family = binomial)
#   step_labour_interaction[[i]] <- step(full_glm, direction = "both")
# }
# save(step_comp_interaction, file = paste(sure_path,
#                                            "/data/step_labour_interaction.Rdata", sep = ""))
```

#Classification Trees
##CART:
###The models using isForcedLabour as response variable
```{r}
tree_labour_list <- mno_regression(data_list[["data_corrected"]][["training"]], 
               imp_formula_labour, rpart)

#Creating a confusion Matrix:
caret::confusionMatrix(predict(tree_labour_list[[1]], 
                               newdata = data_list[["data_corrected"]][["test"]][[1]], 
                               type = "class"), 
                       data_list[["data_corrected"]][["test"]][[1]][["isForcedLabour"]])
```

###The model using isSexualExploit as response variable
```{r}
tree_sex_list <- mno_regression(data_list[["data_corrected"]][["training"]], 
               imp_formula_sex, rpart)

#Creating a confusion Matrix:
caret::confusionMatrix(predict(tree_sex_list[[1]], 
                               newdata = data_list[["data_corrected"]][["test"]][[1]], 
                               type = "class"), 
                       data_list[["data_corrected"]][["test"]][[1]][["isSexualExploit"]])
```

###The model using the composite variable as response variable
```{r}
tree_comp_list <- mno_regression(data_list[["data_corrected"]][["training"]], 
               imp_formula_comp, rpart)

#Creating a confusion Matrix:
caret::confusionMatrix(predict(tree_comp_list[[1]], 
                               newdata = data_list[["data_corrected"]][["test"]][[1]], 
                               type = "class"), 
                       data_list[["data_corrected"]][["test"]][[1]][["isForcedLabour"]])
```


##Random Forest
###The models using isForcedLabour as response variable
```{r}


rf_labour <- mno_regression(data_list[["data_corrected"]][["training"]], imp_formula_labour,
                            randomForest, na.rm = TRUE, cols = "isForcedLabour")

```


###The models using isSexualExploit as response variable
```{r}
rf_sex <- mno_regression(data_list[["data_corrected"]][["training"]], imp_formula_sex,
                            randomForest, na.rm = TRUE, cols = "isSexualExploit")
```



