---
title: "Stratifying individual data set"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing data set and packages
```{r}
library(tidyverse)
sure_path <- substr(getwd(), 1, nchar(getwd()) - 4)
individual_path <- paste(sure_path, "/data/individual_database.csv", sep = "")
individual <- read_csv(individual_path, 
                       col_types = cols(X1 = col_skip(), 
                                        meansOfControlRestrictsFinancialAccess = col_integer(), 
                                        meansOfControlSexualAbuse = col_integer(), 
                                        meansOfControlUsesChildren = col_integer(), 
                                        typeOfSexPornography = col_integer(), 
                                        typeOfSexRemoteInteractiveServices = col_integer(), 
                                        typeOfSexPrivateSexualServices = col_integer()))

#converts year of registration and ageBroad into ordered factors
individual$yearOfRegistration <- as.ordered(individual$yearOfRegistration)
individual$ageBroad <- as.ordered(individual$ageBroad)
individual$ageBroad <- fct_relevel(individual$ageBroad, "0--8", "9--17", 
                                   "18--20", "21--23", "24--26", "27--29", 
                                   "30--38", "39--47", "48+")

#converts the columns with characters into unordered factors
factor_cols <- c("Datasource", "gender", "majorityStatus", "majorityEntry", 
                 "citizenship", "RecruiterRelationship", "CountryOfExploitation")

for (column in factor_cols){
  individual[,column] <- as.factor(unlist(individual[,column]))
}



```

## Stratifying the individual data set

Stratifying the sample by citizenship, CountryOfExploitation, gender, and ageBroad.
Distribution of the number of observations in each strata:
```{r, warning= FALSE}
strat1 <- individual %>% 
  group_by(citizenship, CountryOfExploitation, gender,  ageBroad) %>% 
  summarise(n = n())
ggplot(strat1, aes(x = n)) + geom_histogram() + 
  scale_x_log10(minor_breaks = c(seq.int(20, 90, 10), seq.int(200, 900, 100),
                                 seq.int(2000, 5000, 1000)))

summary(strat1$n)
```

Looking at the strata with 15 or fewer observations
```{r}
strat1[strat1$n <= 15,]
```

Stratifying the sample by citizenship, CountryOfExploitation, gender, ageBroad, 
and RecruiterRelationship.
Distribution of the number of observations in each strata:

```{r}
strat2 <- individual %>% 
  group_by(citizenship, CountryOfExploitation, gender, ageBroad, RecruiterRelationship) %>% 
  summarise(n = n())
ggplot(strat2, aes(x = n)) + geom_histogram() + 
  scale_x_log10(minor_breaks = c(seq.int(20, 90, 10), seq.int(200, 900, 100),
                                 seq.int(2000, 5000, 1000)))

summary(strat2$n)
```

```{r}

```


```{r}
#Work in progress:
#A function to combine the small strata with similar strata.
s1 <- strat1[strat1$n <= 15,]
s2 <- strat1[strat1$n > 15, ]

distance <- double()
for (i in 1:nrow(s2)){
  distance <- c(distance, simple_distance(s1[1,], s2[i,]))
}

simple_distance <- function(entry1, entry2) {(entry1[1:3] != entry2[1:3]) %>%
    .^2 %>% 
    sum() %>% 
  + (as.integer(entry1[4]) - as.integer(entry2[4]))^2.
}

distance <- double()
a <- 31
for (i in 1:nrow(s2)){
  distance <- c(distance, simple_distance(s1[a,], s2[i,]))
  }
```

